---
title: "Treatment-control comparisons in platform trials including non-concurrent controls"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This repository contains the main code to reproduce the results of the paper "Treatment-control comparisons in platform trials including non-concurrent controls''. 
<!-- "[Treatment-control comparisons in platform trials including non-concurrent controls](https://arxiv.org)". -->

This repository is structured as follows:

- Folder **main_paper**:

    - *simscript.R*: This script contains the code to reproduce the simulations for calibration of the Time Machine and MAP Prior shown in Figure 4 in the main paper, and all simulations that use the calibration for the Time Machine assuming an expected change of 1 and a maximal change of 1.5. After running the script, the results for the individual scenarios are then saved in the subfolder *results*.
    - *plots_paper.Rmd*: This file contains the code to create all figures for scenarios that use the above mentioned calibration of the Time Machine. That includes all figures in the main paper, and Figures 1 and 2 in the supplementary material. The figures are saved in the subfolder *figures*.
    

- Folder **supp_material**:

    This folder has an analogous structure as **main_paper**, but for the simulations, an expected change of 0.01 and a maximal change of 0.15 were used for the Time Machine calibration. The resulting plots can be found in the supplementary material (Figures 3-6).

## NCC R-package

The version of the `NCC` [R-package](https://pavlakrotka.github.io/NCC/) that was used for the simulation study is included in this repository.

This version is labeled as Release 1.2 on [GitHub](https://github.com/pavlakrotka/NCC) and can be installed by running the following code:

```{r, message=FALSE, warning=FALSE, results=FALSE, eval=FALSE}
# install.packages("devtools") 
devtools::install_github("pavlakrotka/NCC@v1.2", force = TRUE, build_vignettes = TRUE)
```

------------------------------------------------------------------------

**Funding**

[EU-PEARL](https://eu-pearl.eu/) (EU Patient-cEntric clinicAl tRial pLatforms) project has received funding from the Innovative Medicines Initiative (IMI) 2 Joint Undertaking (JU) under grant agreement No 853966. This Joint Undertaking receives support from the European Union’s Horizon 2020 research and innovation programme and EFPIA and Children’s Tumor Foundation, Global Alliance for TB Drug Development non-profit organisation, Spring works Therapeutics Inc. This publication reflects the authors’ views. Neither IMI nor the European Union, EFPIA, or any Associated Partners are responsible for any use that may be made of the information contained herein.

This research was funded in whole or in part by the Austrian Science Fund (FWF) [ESP 442 ESPRIT-Programm].